Calculating Entropies With Nested Sampling

### 2017-02-09 paper/ms.tex
Some sinusoidal results

$A$ and $\phi$ are nuisance parameters. Let $\x = \log_{10} T$.
The prior standard deviation of the noise, $\sigma$, was set to 0.1.
These results were computed using a tolerance of 0.001 for every quantity.
Results:

% These were produced with a random number seed of 0
% on commit 44525f13edd0d29de43e703db17c594fc0d5045c

\begin{align}                  % (num_particles, mcmc_steps, max_depth, reps)
H_{\x}    &= 6.223 \pm 0.021 \\% (100, 1000, 20.0,  147)
H_{\d}    &= 805.1 \pm 9.7   \\% (100, 1000, 1000.0, 52)
H_{\x,\d} &= 873   \pm 25    \\% (100, 1000, 1200.0, 12)
\end{align}

{\query The multimodality of the posterior in this problem (sometimes) might
affect mixing sufficiently that the NS gets the incorrect answer. Be
careful! And maybe use an example where this is unlikely.}

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-782.02$, and
$-788.23$ respectively.
%\begin{align}
%H'_{\x}     &= 1.113 \pm 0.025 \\
%H'_{\d}     &= 178.4 \pm 3.7   \\
%H'_{\x, \d} &= 180.4 \pm 3.4
%\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong. Update: well I found a bug after this, so it might
change. :)}

The mutual information is equal to $H_{\x} + H_{\d} - H_{\x, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\x, \d}$ if computed naively. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.

>>>>

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for every quantity.
The results were
\begin{align}
H_{\tau}    &= 7.337 \pm 0.028 \\
H_{\d}      &= 904.9 \pm 5.4   \\ % Interim result only
H_{\tau,\d} &= 900.4 \pm 4.7      % Interim result only
\end{align}

{\query The multimodality of the posterior in this problem (sometimes) might
affect mixing sufficiently that the NS gets the incorrect answer. Be
careful! And maybe use an example where this is unlikely, or double
check it using brute force.}

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-790.32$, and
$-796.53$ respectively, so the differential entropies are:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 % \\
%H'_{\d}       &= 178.4 \pm 3.7   \\
%H'_{\tau, \d} &= 180.4 \pm 3.4
\end{align}
The mutual information is equal to $H_{\tau} + H_{\d} - H_{\tau, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\tau, \d}$ if computed naively. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
The resulting mutual information is
$I_{\tau, \d} = 12.1 \pm 3.1$ nats {\todo (interim result only)}.
